You are the way you structurally talk: structural-temporal neighbourhoods of posts to characterize users in online forums

### 2016-04-12 doc/IEEEtran/paper_IEEEformat.tex
cleaning

@@

@@

\subsection{Podemos forum}
Our dataset consists of all posts from March 2014 to May 2015 of the Podemos forum in Reddit\footnote{https://www.reddit.com/r/podemos}\footnote{I have also the data for \textit{gameofthrones, france, datascience, machinelearning complexsystems, philosophy, twoxchromosomes, trees, sex}}. The Podemos forum was conceived in March 2014 as a tool for internal democracy, and forum members used it to debate ideological and organizational principles that were later formalized in their first party congress hold in Madrid the October 18th and 19th 2014. Nowadays, its members use it mainly to share and discuss about political news.
The forum contains 83,6119 posts spread over 47,803 threads and written by 26,193 users. (see Figure~\ref{fig:podemos_distributions})

\begin{figure*}
\centering
\includegraphics[width=0.5\textwidth]{threads_length}%
\includegraphics[width=0.5\textwidth]{users_posts}
\includegraphics[width=0.5\textwidth]{threads_length_cum}%
\includegraphics[width=0.5\textwidth]{users_posts_cum}
\caption{Log-log and cumulative distributions and of thread lengths and posts per user.}
\label{fig:podemos_distributions}
\end{figure*}

 %\noindent\textcolor{red}{\rule{16cm}{1mm}}
\subsection{Counting neighorhoods}
In this section we will build a matrix $M$ for one of the forums of Reddit and then we will cluster users to find groups that have similar preferences over the different types of conversations represented by the neighbourhood structures.

If we set the a spatial radius $r=1$ and an order $n=4$, the temporal neighbourhood $N_{G}^{(t)}(i, 1, 4)$ recovers the four adjacent posts that were written temporally closest to a given post. Figure~\ref{fig:neighbourhoods_1_4} shows the four detected neighbourhoods and their frequency.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{neighbourhoods_1_4}
	\caption{neighbourhood counts with $r=1$ and $n=4$}
	\label{fig:neighbourhoods_1_4}
\end{figure*}

@@

\subsection{Clustering}

@@

>>>>

\section{Data}

@@

\subsection{Neighbourhood pruning}\label{sec:pruning}

@@

Our dataset consists of all posts from March 2014 to May 2015 of the Podemos forum in Reddit\footnote{https://www.reddit.com/r/podemos}\footnote{I have also the data for \textit{gameofthrones, france, datascience, machinelearning complexsystems, philosophy, twoxchromosomes, trees, sex}}. The Podemos forum was conceived in March 2014 as a tool for internal democracy, and forum members used it to debate ideological and organizational principles that were later formalized in their first party congress hold in Madrid the October 18th and 19th 2014. Nowadays, its members use it mainly to share and discuss about political news.
The forum contains 83,6119 posts spread over 47,803 threads and written by 26,193 users. (see Figure~\ref{fig:podemos_distributions})

\begin{figure*}
\centering
\includegraphics[width=0.5\textwidth]{users_posts}%
\includegraphics[width=0.5\textwidth]{users_posts_cum}
\caption{Log-log and cumulative distributions and of posts per user.}
\label{fig:podemos_distributions}
\end{figure*}

 %\noindent\textcolor{red}{\rule{16cm}{1mm}}
\subsection{Neighbourhood census}
In this section we analyse the neighbourhood census of our dataset. A counter for every neighbourhood structure is created the first time we detect them. For every post, we extract its neighbourhood (order-based or time-based) and prune it as explained above (Section~\ref{sec:pruning}). Then check whether it is isomorphic to some of the already seen neighbourhoods. If this is the case, then we increment the counter for the neighbourhood previously seen. Otherwise we create a new entry for the current neighbourhood.

\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{census_orderbased_1}
	%\includegraphics[width=0.8\textwidth]{census_orderbased_2}
	%\includegraphics[width=0.8\textwidth]{census_orderbased_3}
	\caption{Most frequent order-based neighbourhoods with $r=2$ and $n=4$}
	\label{fig:census_orderbased}
\end{figure*}

The census obtained with both type of neighbourhood are similar for the most frequent structures. That means that both kind of neighbourhoods are isomorphic for the most popular discussion structures.

In this section we will build a matrix $M$ for one of the forums of Reddit and then we will cluster users to find groups that have similar preferences over the different types of conversations represented by the neighbourhood structures.

@@

@@

\subsection{Conversation-based clustering of users}

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{PCA_cluster_timebased}
	\includegraphics[width=1\textwidth]{PCA_cluster_orderbased}
	\caption{PCA projection of the clusters found and cluster profile in every dimension.}
	\label{fig:PCA}
\end{figure*}
